### 2023-01-25 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@c1b6843af19aa07ac594d30f93b6f812201d80f0 🚀

\begin{figure}
\hypertarget{fig:embedding}{%
\centering
\includegraphics{figures/conceptual_2.png}
\caption{The embedding process (\textbf{A}) can help to identify links
(interactions) that may have been missed within the original community
(represented by the orange dashed lines, \textbf{B}). Transfer learning
allows for the prediction links (interactions) when novel species
(\textbf{C}) are included alongside the original community (\textbf{D}).
This is achieved by learning using other relevant predictors
(\emph{e.g.} traits) in conjunction with the known interactions to infer
latent values (\textbf{E}). Ultimately this allows us to predict links
(interactions) for species external to the original sample as well as
within sample links (\textbf{F}). Within this context the predicted (and
original) networks as well as the ecological predictors used (green
boxes) are products that can be quantified through field measurements,
whereas the embedded as well as imputed matrices are representative of a
decomposition of the interaction networks}\label{fig:embedding}
}
\end{figure}

>>>>

\begin{figure}
\hypertarget{fig:embedding}{%
\centering
\includegraphics{figures/conceptual_2.png}
\caption{The embedding process (\textbf{A}) can help to identify links
(interactions) that may have been missed within the original community
(represented by the orange dashed lines, \textbf{B}). Transfer learning
allows for the prediction links (interactions) when novel species
(\textbf{C}) are included alongside the original community (\textbf{D}).
This is achieved by learning using other relevant predictors
(\emph{e.g.} traits) in conjunction with the known interactions to infer
latent values (\textbf{E}). Ultimately this allows us to predict links
(interactions) for species external to the original sample as well as
within sample links (\textbf{F}). Within this context the predicted (and
original) networks as well as the ecological predictors used (green
boxes) are products that can be quantified through field measurements,
whereas the embedded as well as imputed matrices (purple box) are
representative of a decomposition of the interaction
networks}\label{fig:embedding}
}
\end{figure}
